%-------------------------
% ATS-Friendly Resume – Pola Manoj Kumar
% Compiler: XeLaTeX or pdfLaTeX (Overleaf default)
%-------------------------
\documentclass[10pt, a4paper]{article}

\usepackage[
  top=12mm, bottom=10mm,
  left=14mm, right=14mm
]{geometry}

\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{array}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{parskip}

% ── Hyperlink styling ──────────────────────────────────────────────
\hypersetup{
  colorlinks=true,
  urlcolor=blue!60!black,
  linkcolor=blue!60!black
}

% ── No page numbers ────────────────────────────────────────────────
\pagestyle{empty}

% ── Section heading style ──────────────────────────────────────────
\definecolor{accent}{RGB}{26, 58, 92}

\titleformat{\section}
  {\large\bfseries\color{accent}}
  {}{0em}{}
  [\color{accent}\titlerule]

\titlespacing{\section}{0pt}{6pt}{4pt}

% ── Helpers ────────────────────────────────────────────────────────
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

\newcommand{\resumeItem}[1]{%
  \item\small{#1}
}

\newcommand{\jobheading}[4]{%
  \noindent
  \begin{tabularx}{\linewidth}{@{}X r@{}}
    \textbf{#1} $|$ \textit{#2, #3} & \small\textit{#4}
  \end{tabularx}
  \vspace{-2pt}
}

\newcommand{\projectheading}[2]{%
  \noindent
  \begin{tabularx}{\linewidth}{@{}X r@{}}
    \textbf{#1} & \small\href{#2}{\underline{GitHub}}
  \end{tabularx}
  \vspace{-2pt}
}

\newcommand{\projectheadingnl}[1]{%
  \noindent\textbf{#1}
  \vspace{-2pt}
}

\newenvironment{itemizeCustom}{%
  \begin{itemize}[leftmargin=12pt, itemsep=1pt, topsep=2pt, parsep=0pt]
}{%
  \end{itemize}
}

%===================================================================
\begin{document}
%===================================================================

% ── NAME & CONTACT ─────────────────────────────────────────────────
\begin{center}
  {\LARGE\bfseries\color{accent} Pola Manoj Kumar}\\[4pt]
  \small
  +91 82176 75741 \;$|$\;
  \href{mailto:manojkumar.mk0965@gmail.com}{manojkumar.mk0965@gmail.com} \;$|$\;
  Bangalore, India \\[2pt]
  \href{https://www.linkedin.com/in/pola-manoj-kumar-30b528306}{LinkedIn}
  \;$|$\;
  \href{https://github.com/manojkumar675}{GitHub}
  \;$|$\;
  \href{https://leetcode.com/u/ManojKumar675/}{LeetCode}
\end{center}

\vspace{-4pt}

% ── PROFESSIONAL SUMMARY ───────────────────────────────────────────
\section{Professional Summary}
Full Stack Developer (MERN) with hands-on experience building and deploying responsive
web applications. Proficient in Java, Python, React.js, Node.js, and RESTful API integration.
Practical knowledge of DevOps practices including CI/CD pipelines, Docker, AWS cloud
deployment, and Linux environments. Experienced with ML model development using
Scikit-learn and BERT. Seeking a Full Stack Developer role to deliver scalable,
user-centric software solutions.

% ── TECHNICAL SKILLS ───────────────────────────────────────────────
\section{Technical Skills}
\begin{tabularx}{\linewidth}{@{} >{\bfseries}l X @{}}
  Languages       & Java, JavaScript (ES6+), Python \\[2pt]
  Frontend        & React.js, HTML5, CSS3, Responsive Design \\[2pt]
  Backend         & Node.js, Express.js, REST APIs \\[2pt]
  Database        & MongoDB, SQL \\[2pt]
  DevOps \& Cloud & Docker, CI/CD (Jenkins / GitHub Actions), AWS (EC2, S3), Linux, Git, Postman \\[2pt]
  ML / AI         & Scikit-learn, Random Forest, Logistic Regression, BERT, Streamlit \\[2pt]
  Concepts        & Data Structures \& Algorithms, OOP, DBMS, System Design, Agile \\
\end{tabularx}

% ── WORK EXPERIENCE ────────────────────────────────────────────────
\section{Work Experience}

\jobheading{Technical Trainee – Java Full Stack \& DevOps}{Dhee Coding Lab}{Bangalore}{Feb 2026 – Present}
\begin{itemizeCustom}
  \resumeItem{Developing proficiency in Core Java, OOP principles, and Data Structures \& Algorithms through structured hands-on training.}
  \resumeItem{Implemented CI/CD pipelines using Jenkins and GitHub Actions; containerised applications with Docker and deployed to cloud environments.}
  \resumeItem{Configured Linux servers, managed Git-based version control workflows, and applied DevOps lifecycle best practices including monitoring and rollback strategies.}
\end{itemizeCustom}

% ── INTERNSHIP EXPERIENCE ──────────────────────────────────────────
\section{Internship Experience}

\jobheading{Web Development Intern}{Prinston Smart Engineers – Myntrn Technology}{Bangalore}{Jul 2024 – Aug 2024}
\begin{itemizeCustom}
  \resumeItem{Built and deployed 5+ responsive web pages using React.js, Node.js, Express.js, HTML5, and CSS3, improving UI consistency across the application.}
  \resumeItem{Integrated 3+ RESTful APIs and engineered backend logic with Express.js, reducing manual data handling and improving response efficiency.}
  \resumeItem{Collaborated in an Agile team to ship features on schedule and resolve production issues, contributing to a smoother end-user experience.}
\end{itemizeCustom}

% ── PROJECTS ───────────────────────────────────────────────────────
\section{Projects}

\projectheading{BERT-Based Multilingual Medical Chatbot with Hospital Finder}{https://github.com/manojkumar675}
\begin{itemizeCustom}
  \resumeItem{Built a full-stack web app delivering multilingual medical advice using BERT for semantic text matching and Streamlit for an interactive UI.}
  \resumeItem{Integrated a real-time hospital locator with geolocation-based filtering and mapping, connecting users with nearby healthcare facilities instantly.}
\end{itemizeCustom}

\vspace{4pt}

\projectheading{Automated CI/CD Deployment Pipeline}{https://github.com/manojkumar675}
\begin{itemizeCustom}
  \resumeItem{Designed an end-to-end CI/CD pipeline using Jenkins and GitHub Actions to automate build, test, and deployment workflows, reducing manual effort significantly.}
  \resumeItem{Containerised a Node.js application with Docker and deployed to AWS EC2 with staging and production environment separation; configured monitoring and rollback strategies.}
\end{itemizeCustom}

\vspace{4pt}

\projectheading{Student Record Manager (MERN Stack)}{https://github.com/manojkumar675}
\begin{itemizeCustom}
  \resumeItem{Designed and deployed a full CRUD application using MongoDB, Express.js, React.js, and Node.js with JWT-based authentication and a clean responsive UI.}
\end{itemizeCustom}

% ── EDUCATION ──────────────────────────────────────────────────────
\section{Education}

\begin{tabularx}{\linewidth}{@{} X r @{}}
  \textbf{B.E. – Information Science \& Engineering} & \textit{2022 – Present (Expected 2026)} \\
  AMC Engineering College, Bangalore \hspace{4pt} CGPA: 7.94 / 10 & \\[4pt]
  \textbf{SSLC} & \textit{Mar 2020} \\
  Sri Chaitanya Techno School, Anantapur \hspace{4pt} Score: 100/100 & \\
\end{tabularx}

% ── CERTIFICATIONS ─────────────────────────────────────────────────
\section{Certifications}
\begin{itemizeCustom}
  \resumeItem{\textbf{Full Stack Web Development} – Myntrn Technology \hfill \textit{Jul 2024}}
  \resumeItem{\textbf{DSA using Java} – NPTEL \hfill \textit{Jan – Oct 2024}}
  \resumeItem{\textbf{AWS Solutions Architecture} – Forage \hfill \textit{Mar 2025}}
  \resumeItem{\textbf{IBM Watson Text-to-Speech} – IBM SkillsBuild \hfill \textit{Oct 2024}}
\end{itemizeCustom}

% ── LANGUAGES ──────────────────────────────────────────────────────
\section{Languages}
\small English (C1 – Advanced) \;$|$\; Telugu (C2 – Fluent) \;$|$\; Kannada (C2 – Fluent) \;$|$\; Hindi (B2 – Intermediate)

\end{document}
